Flexible Scientific Data Management for Plant Phenomics Research

### 2013-03-11 s4biodiv2013/PODD-S4BIODIV-Submission.tex
cut back to 8 pages by reducing details in the introduction

To achieve this goal, the vast array of phenotypic data collected from a variety
of phenomics platforms must be combined with metadata explaining how the raw
information was collected. This process forms structured digital objects
containing the raw information. These objects are then delivered to a range of
analysis pipelines, which transform the raw information into  aggregated
multi-phase datasets, each phase representing a new aggregation or inference
from the original raw data. This reduction process converts the raw
multi-dimensional data into information which is conceptually interpretable by a
human being, i.e. new knowledge. The details about the steps taken are recorded
to give context to the data. These links enable scientists to generate novel
conclusions about the plants being phenotyped, including conclusions based on
the genotype, plant growth environments, treatments, phenotyping platforms and
the phenotyping and analysis processes.

@@

Thus, to support publicly-funded phenomics activities in Australia, the
Phenomics Ontology Driven Data repository (PODD) has been developed as a
repository for data produced by the variety of plant imaging and phenotyping
platforms available at the High Resolution Plant Phenomics Centre, as well as
for recording the contextual metadata associated with plant genotypes,
treatments and environmental conditions \cite{Li2010}. PODD manages the links between the
raw image files generated by plant imaging platforms, the results from analyses,
and conclusions by scientists.

>>>>

To achieve this goal, the vast array of phenotypic data collected from a variety
of phenomics platforms must be combined with metadata explaining how the raw
information was collected. This process forms structured digital objects
containing the raw information. These objects are then delivered to a range of
analysis pipelines, which transform the raw information into  aggregated
multi-phase datasets, each phase representing a new aggregation or inference
from the original raw data. This reduction process converts the raw
multi-dimensional data into information which is conceptually interpretable by a
human being, i.e. new knowledge. The details about the steps taken are recorded
to give context to the data. 
% These links enable scientists to generate novel
% conclusions about the plants being phenotyped, including conclusions based on
% the genotype, plant growth environments, treatments, phenotyping platforms and
% the phenotyping and analysis processes.

@@

Thus, to support publicly-funded phenomics activities in Australia, the
Phenomics Ontology Driven Data repository (PODD) has been developed as a
repository for data produced by the variety of plant imaging and phenotyping
platforms available at the High Resolution Plant Phenomics Centre, as well as
for recording the contextual metadata associated with plant genotypes,
treatments and environmental conditions \cite{Li2010}. 
% PODD manages the links between the
% raw image files generated by plant imaging platforms, the results from analyses,
% and conclusions by scientists.
